Collaborative Visual Analysis on the Web with RCloud

### 2015-06-16 introduction.tex
yes

Computing has moved far beyond what Tukey imagined.
Processing and networking capabilities today far exceed
what was barely imaginable then. Sophisticated technologies
for processing, storing, publishing, searching and sharing
information and analyses are commonplace.
But how we \emph{develop} analytic solutions has not changed much. 
Although environments such as RStudio include many features to
graphically interact with a local workspace, still follow the metaphor
of terminal, text editor, and source files stored in file systems.

>>>>

Computing has moved far beyond what Tukey imagined.
Processing and networking capabilities today far exceed
what was barely imaginable then. There has been a lot of
work on distributed computing frameworks, and social computing
technologies for publishing, searching and sharing information
are common on the internet.
But how we \emph{develop} analytic solutions has not changed much. 
Although environments such as RStudio include many features to
graphically interact with a local workspace, they still follow the
metaphor of terminal, text editor, and source files stored in file systems.
